The French Covid-19 vaccination policy did not solve vaccination inequities: a nationwide longitudinal study on 64.5 million individuals

### 2022-07-08 ms/figs.Rmd
add description labels
format supp table

stb <- merge(supptab, txt, by = "predictor", all.x = TRUE)
stb

# Save as csv
write.csv(stb, file = "../ms/SuppTable_OR_wide.csv", row.names = FALSE)

>>>>

# Merge the tables to add the descriptions
stb <- merge(supptab, txt, by = "predictor", all.x = TRUE)

#------------------------
# Add median and N
tmp <- read.csv("../data/insee_indicators_n_med_iqr_minmax.csv", sep = ";")
names(tmp)[1] <- "predictor"
# Remove "X" at start of name
iX <- which(substr(tmp$predictor, 1, 1) == "X") # Lines with "X"
tmp[iX, "predictor"] <- vapply(tmp[iX, "predictor"], FUN = function(x) substr(x, 2, nchar(x)), FUN.VALUE = "x") # Remove "X" on these lines
# Check that we have all labels
all(is.element(supptab$predictor, tmp$predictor))

# Merge the tables to add the values
stb <- merge(stb, tmp, by = "predictor", all.x = TRUE)
# Reorder columns
stb <- stb[, c(1, 2, 9, 10, 11, 12, 3:8)]

# Save as csv
write.csv(stb, file = "../ms/SuppTable_OR_wide.csv", row.names = FALSE)
```
